Social Class and Naming Patterns in Chile: Imitation and Differentiation

### 2024-02-24 text/extended_abstract_ASA.tex
Updates from Overleaf

>>>>

\begin{figure}[H]
\begin{center}
    \includegraphics[width=12cm]{plot/q5_q4_comparison.png}
    \caption{Overlap top names (n=10) between Q5 and Q4 by decade}
    \label{fig:new_names}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
    \includegraphics[width=12cm]{plot/q5_q3_comparison.png}
    \caption{Overlap top names (n=10) between Q5 and Q3 by decade}
    \label{fig:new_names}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
    \includegraphics[width=12cm]{plot/q5_q2_comparison.png}
    \caption{Overlap top names (n=10) between Q5 and Q2 by decade}
    \label{fig:new_names}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
    \includegraphics[width=12cm]{plot/q5_q1_comparison.png}
    \caption{Overlap top names (n=10) between Q5 and Q1 by decade}
    \label{fig:new_names}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
    \includegraphics[width=12cm]{plot/Q5_all_comparison.png}
    \caption{Overlap top names (n=10) between Q5 and Qx by decade}
    \label{fig:new_names}
\end{center}
\end{figure}
